\documentclass{mincv}

\cvname{Arthur}{Bean}
\cvjob{Head Barista \& Specialty Roaster}
\cvlocation{Seattle, WA}
\cvemail{arthur.brew@example.com}
\cvphone{+1 (555) 019-2834}
\cvgithub{https://github.com/arthurbean123} 
\cvlinkedin{https://linkedin.com/in/arthurbean123}
%\cvphoto{profile} 

\begin{document}

\makecvheader

\section{Experience}

\begin{cventry}{Lead Roaster \& Barista}{The Grind Lab}{2022 -- Present}{Seattle, WA}
    \item Oversee roasting operations for a high-volume cafe, processing 500kg+ of green coffee weekly while maintaining strict QC standards using Cropster.
    \item Established direct trade partnerships with three farms in Huila, Colombia, securing exclusive micro-lots and ensuring 20\% above-market wages for farmers.
\end{cventry}

\begin{cventry}{Senior Barista}{Midnight Espresso Bar}{2019 -- 2022}{Portland, OR}
    \item Managed opening procedures for a fast-paced downtown location, serving 300+ customers daily with an average ticket time of under 3 minutes.
    \item Redesigned the bar workflow to optimize ergonomics, resulting in a 15\% increase in peak-hour efficiency.
\end{cventry}

\section{Projects}

\begin{cventryshort}{Pop-Up: "The Zero Waste Cafe"}{Summer 2023}
    \item Launched a temporary weekend pop-up focused on zero-waste practices, utilizing compostable cups and a coffee-husk recycling program.
    \item Generated \$15,000 in revenue over 8 weekends and was featured in "Seattle Coffee Culture".
\end{cventryshort}

\begin{cventryshort}{Regional Aeropress Championship}{2021}
    \item Secured 2nd place against 40 competitors with a custom immersion brewing recipe utilizing a rare Geisha varietal.
\end{cventryshort}

\section{Education}

\begin{cventry}{B.A. Hospitality Management}{University of Oregon}{2015 -- 2019}{Eugene, OR}
    \item \textbf{Thesis:} "Sustainable Supply Chains in the Global Coffee Industry"
    \item \textbf{Coursework:} Operations Management, Financial Accounting, Business Ethics.
\end{cventry}

\begin{cventryshort}{SCA Diploma in Coffee Skills}{2020}
    \item Specialty Coffee Association (Score: 98/100)
    \item Modules: Sensory Skills (Professional), Green Coffee, Brewing, and Roasting.
\end{cventryshort}

\section{Skills}

\begin{cvskills}
    \cvskill{Brewing}{Espresso profiling, Pour-over (V60, Kalita), Syphon, Cold Brew}
    \cvskill{Roasting}{Cropster, Green Grading, Sample Roasting, Profile Design}
    \cvskill{Software}{Square POS, Excel (Inventory modeling), Python (Basic data analysis)}
    \cvskill{Languages}{English (Native), Spanish (Professional working proficiency)}
\end{cvskills}

\end{document}